Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-31 parts/intro.tex
some changes

This paper is organized as follows:
Section~\ref{sec:candidates_models} introduces the candidates, the models and the diagnostics applied to them.
The following sections elaborate on the diagnostics.
Image morphology diagnostics are explained in Section~\ref{sec:morph} and
diagnostics based on the mass models in Section~\ref{sec:massmodels}.
Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the lensing candidates.
Section~\ref{sec:summary} summarises and tabulates the diagnostics in
Table~\ref{tab:models}.

@@

\SW is a citizen science gravitational lens search \citep{2016MNRAS.455.1171M}.
Its first run searched the CFHT Legacy Survey, a survey carried out in five optical bands ($u^*$,$g'$,$r'$,$i'$,$z'$) covering a total area of 160 \sqdeg, divided up into four fields.
It has a field of view of 1 \sqdeg, a pixel size of 0.186'' and the deepest limiting magnitude is 25.47 in the $g$ band\citep{2012AJ....143...38G}.
The cutouts shown to the volunteers were colour composites of the $g$, $r$ and $i$ band of randomly chosen regions.
It resulted in 59 new (of which 29 promising) lens candidates that have not been found by other searches already and in the rediscovery of 82 previously known lens candidates.
The candidates have broadly similar redshifts (0.2 -- 1.0), Einstein radii (0.7\arcsec -- 5\arcsec) and arc magnitudes (22 -- 26) as previous robotic robotic searches by ArcFinder and RingFinder \citep{2016MNRAS.455.1191M}.

\begin{figure}
  \includegraphics[width=\linewidth]{img/timelapse3}
  \caption{ Number of models generated over time in days since an arbitrary starting point; black line shows all models, colored lines show five most active candidates. Total of 365 models were generated for 56 lens candidates, eight users contributed more than five models per person. }
  \label{fig:time}
\end{figure}

While \SW was running, volunteers started working with \SpL to create models of possible lensing candidates found in \SW that were debated on the \SW discussion forums, before they were classified as plausible candidates.
Figure~\ref{fig:time} shows the total number of models generated over time, models created for systems that turned out to be non candidates were not included.
The first beta version of \SpL was launched in May 2013 and additional features were implemented on the fly.
The system was tested by eight major contributors, volunteers that at least generated five models.
In the beginning of August 2013 (day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
In April 2015 (day 700) the first full version of \SpL was presented for testing.
In the same time the list of identified candidates was made available \citep[as a preprint of the later work][]{2016MNRAS.455.1191M}.
At this stage, the volunteers were asked to complete the sample and to create models for all the lens candidates that were still missing.
The generated models for candidate \sw{29} show that the volunteers converged to a favorable model much faster, after 15 models generated in 30 days.
This modelling effort resulted in a set of 377 \SpL models for all but one of the \SW 59 lens candidates; candidate \sw{39} was not modelled.

\cite{2015MNRAS.447.2170K} tested the system
on simulated lenses and identified some areas for improvement.  In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass profile to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

>>>>

This paper is organized as follows:
Section~\ref{sec:candidates_models} introduces the candidates, the models and the diagnostics applied to them.
The following sections elaborate on the diagnostics.
Image morphology diagnostics are explained in Section~\ref{sec:morph} and
diagnostics based on the mass models in Section~\ref{sec:massmodels}.
Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the candidates.
Section~\ref{sec:summary} summarises and tabulates the diagnostics in
Table~\ref{tab:models}.

@@

\SW is a citizen science gravitational lens search \citep{2016MNRAS.455.1171M}.
Its first run searched the CFHT Legacy Survey, a survey carried out in five optical bands ($u^*$,$g'$,$r'$,$i'$,$z'$) covering a total area of 160 \sqdeg divided up into four fields W1 -- W4.
It has a field of view of 1 \sqdeg, a pixel size of 0.186'' and the deepest limiting magnitude is 25.47 in the $g$ band \citep{2012AJ....143...38G}.
The cutouts shown to the volunteers were colour composites of the $g$, $r$ and $i$ band of randomly chosen regions.
It resulted in 59 new (of which 29 promising) lens candidates that have not been found by other searches already and in the rediscovery of 82 previously known lens candidates.
The candidates have broadly similar redshifts (0.2 -- 1.0), Einstein radii (0.7\arcsec -- 5\arcsec) and arc magnitudes (22 -- 26) as those found by previous robotic searches like ArcFinder and RingFinder \citep{2016MNRAS.455.1191M}.

\begin{figure}
  \includegraphics[width=\linewidth]{img/timelapse3}
  \caption{ Number of models generated over time in days since the launch of \SpL; the black line shows all models, the coloured lines show the five most active candidates. A total of 377 models were generated for 58 lens candidates, eight users contributed more than five models per person. }
  \label{fig:time}
\end{figure}

A first version of \SpL was launched in May 2013, while the first run of \SW was ongoing.
Figure~\ref{fig:time} shows the total number of models generated since launch, but only includes models for the lens candidates.
A small number of volunteers started to work with \SpL to create models of possible lens candidates found in \SW that were debated on in the \SW discussion forums.
In the beginning of August 2013 (around day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days passed and 30 models have been created for this particular system.
In April 2015 (day 700) the first major release of \SpL was presented.
In the same time the list of identified candidates was made available \citep[as a preprint of][]{2016MNRAS.455.1191M}.
At this stage, the volunteers were asked to create models for all the lens candidates that were still missing.
The generated models for candidate \sw{29} show that the volunteers converged to a favourable model much faster, after 15 models generated in 30 days.

This modelling effort resulted in a total set of 377 \SpL models for all but one of the 59 \SW lens candidates; candidate \sw{39} was not modelled by any volunteer.
Over its runtime the system saw eight major contributors (volunteers that at least generated five models each).

In parallel \cite{2015MNRAS.447.2170K} tested the system
on simulated lenses and identified some areas for improvement.  In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass profile to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.
